\needspace{6em}
{\Large {\bf Research Experience}} 
\vspace{0.1cm}
\hrule
\medskip

\needspace{6em}
\begin{tabular*}{7.1in}{@{}l@{\extracolsep\fill}r}
{\large {\bf Recurse Center}} & New York, NY, Sabbatical, 2016\\
\end{tabular*}
Developed game and graphics demos in webGL/Javascript, OpenGL ES/Android, and openCV. Rebuilt website using Python Flask, SQLAlchemy, and Jinja. Mentored for openGL and aided follow recursers in creating their own first ray tracers.

\medskip

\needspace{6em}
\begin{tabular*}{7.1in}{@{}l@{\extracolsep\fill}r}
{\large {\bf University of Pennsylvania}} & Philadelphia, PA, Visiting Research Scholar, 2016\\
\end{tabular*}
Advised students in developing a large, activity rich crowd for a simulaton of Reading Terminal Market.

\medskip

\needspace{6em}
\begin{tabular*}{7.1in}{@{}l@{\extracolsep\fill}r}
   {\large {\bf Wharton Consumer Analytics Initiative (WCAI)}} & Philadelphia, PA, Researcher, 2015\\
\end{tabular*}

Won proposal for ``Discovery of Latent Play Styles for Improved Game Matching and Prediction" to develop and evaluate a novel clustering algorithm for player-vs-player match logs of Battlefield 3 players.

\medskip


\needspace{6em}
\begin{tabular*}{7.1in}{@{}l@{\extracolsep\fill}r}
{\large {\bf Robotics Institute, Carnegie Mellon University}} & Pittsburgh, PA, Research Assistant, 2011-2012\\
\end{tabular*}

Researched algorithms for efficiently collecting data using games within an online, multiplayer environment; user perception of game controllers; and algorithms for animating crowds. 
\medskip

\needspace{6em}
\begin{tabular*}{7.1in}{@{}l@{\extracolsep\fill}r}
{\large {\bf Disney Research}} & Pittsburgh, PA, Imagineering Intern, 2011\\
\end{tabular*}

Researched and developed an animation system for automatically generating character responses dynamically. 
For a given character (possibly robotic or virtual), the resulting system generated 
smooth, collision-free transitions between performance animations and response animations.


